---
title: "Working with GGPLOT2"
output: html_notebook
---
### GGPLOT2


<font color = 'purple'> This is the second assignment of R programming which will focus on basics of R, and using ggplot2. 

\newline You should not use `for loop` in your code snippets unless mentioned specifically.

<font color = 'green'> **Question 1**:

1. Load the built-in dataset `mtcars`.\

2. Using `mtcars`, create a bar chart showing the average miles per gallon `(mpg)` for each number of cylinders `(cyl)`.\

3. customize the bar chart by using a unique color palette and different fill colors for each bar.

Score(10)

```{r}
#Your code starts here






#Your code ends here
```


<font color = 'darkblue'> **Question 2**:

1. Load the built-in dataset `economics`.\

2. Filter the dataset to include data only from the year 2000 onwards.\

3. Create a line chart showing the trend of the unemployment rate `(unemploy)` over time `(date)`.\

4. Customize the line chart by using a 'green' dashed line style and adding a smooth curve to the line.\

Score(10)

```{r}
#Your code starts here






#Your code ends here
```


<font color = 'red'> **Question 3**:

1. Load the built-in dataset `iris`.\

2. Create a scatter plot showing the relationship between sepal length `(Sepal.Length)` and sepal width `(Sepal.Width)` for each species of `iris`.\

3. Customize the scatter plot by using different shapes for each species and a 'color gradient' based on 'sepal length'.\

Score(20)

```{r}
#Your code starts here






#Your code ends here
```

<font color = 'cyan4'> **Question 4**:

1. Load the built-in dataset `diamonds`.

2. Filter the dataset to include only diamonds with a cut of 'Ideal'.

3. Create a histogram showing the distribution of diamond prices `(price)` for 'Ideal' cut diamonds.

4. Customize the histogram by using a 'gradient fill color' and adjusting the 'bin' width for a clearer representation.

Score(20)

```{r}
#Your code starts here






#Your code ends here
```

<font color = 'darkcyan'> **Question 5**:

1. Load the built-in dataset `mpg`.

2. Calculate the average highway mileage (hwy) for each class of vehicles `(class)`.

3. Create a grouped bar chart comparing the average highway mileage of different vehicle classes.

4. Customize the grouped bar chart by using a 'gradient color' scheme for each bar group.
Score(20)


```{r}
#Your code starts here






#Your code ends here
```

<font color = 'aquamarine3'> **Question 6**:

1. Load the built-in dataset `diamonds`.

2. Create a scatter plot showing the relationship between diamond `carat` and `price`, with each cut of the diamond displayed in a separate facet.


3. Customize the scatter plot by:


* Using a color gradient to represent the clarity of the diamonds.


Score(20)

```{r}
#Your code starts here






#Your code ends here
```
